One page description

### 2016-09-23 publications/Journal/models.tex
* removed reference 22

In this section, we evaluate the performance of different synchronization protocols in \textit{dxex}.
We also compare to \textit{adevs}~\cite{adevs}, currently one of the most efficient simulation kernels~\cite{DEVSSurvey,DEVStoneJournal}, to show that our modularity does not impede performance.
CPU time and memory usage is compared for both sequential and parallel simulation.

>>>>

In this section, we evaluate the performance of different synchronization protocols in \textit{dxex}.
We also compare to \textit{adevs}~\cite{adevs}, currently one of the most efficient simulation kernels~\cite{DEVStoneJournal}, to show that our modularity does not impede performance.
CPU time and memory usage is compared for both sequential and parallel simulation.
